---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![R build status](https://github.com/poissonconsulting/poisplot/workflows/R-CMD-check/badge.svg)](https://github.com/poissonconsulting/poisplot/actions)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/poisplot/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/poisplot?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

# poisplot

`poisplot` is an R package of a few utility functions to help with creating ggplot objects for Poisson's projects.

## Demonstration

People often find it easiest to conceptualize an effect size in terms of the percent change.
However, negative percent change (which cannot be less than 100%) does not scale linearly in the same way as positive percent change (which is unlimited).
This results in positive changes appearing much larger than equivalent negative changes in a standard plot.

```{r}
library(poisplot)
library(ggplot2)
library(scales)

data <- data.frame(y = c(-3/4,-2/3,-1/2,0,1,2,3))
data$x <- 1:nrow(data)

gp <- ggplot(data, aes(x = x, y = y)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_line() +
  geom_point()

gp + scale_y_continuous(labels = percent)
```

The `nfold_trans()` function ensures that negative percent changes scale in the same way as positive percent changes.

```{r}
gp + scale_y_continuous(labels = percent, trans = nfold_trans(), breaks = data$y)
```

The poisplot also makes the Poisson plot theme available.
```{r}
gp + scale_y_nfold(labels = percent) +
  theme_Poisson()
```

## Installation

To install from GitHub
```
install.packages("devtools")
devtools::install_github("poissonconsulting/poisplot")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/poisplot/issues).

[Pull requests](https://github.com/poissonconsulting/poisplot/pulls) are always welcome.

## Code of Conduct

Please note that the poisplot project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

